Acceleration of plague outbreaks in the second pandemic

### 2020-07-08 ms_text.tex
changed are apparently'' to appear to be''

For the period since 1540, the existence of multiple sources allows us to cross-check results---in particular, to test our assertion that aggregated counts of wills by date written are an adequate proxy for mortality rates---and avoid relying on any questionable or poorly sampled segments of data \cite{RoosCurt18} (see \supp). In 1563 and 1593, the number of PCC wills is too small to extract a signal from the noise, but the data for the later three outbreaks verify that the numbers of wills written follow the plague epidemic patterns evident in the mortality records (\cref{F:timeseries}). Based on cross-correlation analysis and differences between epidemic peak times, will counts appear to have lagged mortality recorded in parish registers and LBoM by approximately 3--5 weeks; our inferences about epidemic growth rates are apparently robust to this lag (see \supp).

>>>>

For the period since 1540, the existence of multiple sources allows us to cross-check results---in particular, to test our assertion that aggregated counts of wills by date written are an adequate proxy for mortality rates---and avoid relying on any questionable or poorly sampled segments of data \cite{RoosCurt18} (see \supp). In 1563 and 1593, the number of PCC wills is too small to extract a signal from the noise, but the data for the later three outbreaks verify that the numbers of wills written follow the plague epidemic patterns evident in the mortality records (\cref{F:timeseries}). Based on cross-correlation analysis and differences between epidemic peak times, will counts appear to have lagged mortality recorded in parish registers and LBoM by approximately 3--5 weeks; our inferences about epidemic growth rates appear to be robust to this lag (see \supp). 
%%
\ben{I *think* all I meant (no longer 100\% sure) is that, since we get reasonably consistent numbers across the different record types, that suggests that lag doesn't have a big effect. This is of course a weak argument, as we could imagine that we would get different growth rates from the different record types *if* they were not differently lagged, and the lag effects are canceling out the true differences.}
\david{changed ``are apparently'' to ``appear to be''}
